Cover Letter

### 2017-12-12 paper/sections/6_results.tex
benchmark: make source available (#31)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\newcomment{To make our results reproducible, this paper adheres to The Popper
Convention~\cite{jimenez_popper_2016}, so experiments presented here are
available in the repository for this article.  Experiments can be examined in
more detail, or even re-run, by visiting the \texttt{[source]} link next to
each figure. That link points to a Jupyter notebook that shows the analysis and
source code for that graph, which points to an experiment and its artifacts.}
\addressesissue{1}

>>>>

\newcomment{To make our results reproducible, this paper adheres to The Popper
Convention~\cite{jimenez_popper_2016}, so experiments presented here are
available in the repository for this article.  Experiments can be examined in
more detail, or even re-run, by visiting the \texttt{[source]} link next to
each figure. That link points to a Jupyter notebook that shows the analysis and
source code for that graph, which points to an experiment and its artifacts.
The source code is available on the Cudele
branch\footnote{\newcomment{https://github.com/michaelsevilla/ceph/tree/cudele}}
of our Ceph fork.} \addressesissue{1}
